Selección de Servicios Web De Máxima Utilidad Usando Circuitos

### 2009-12-13 tesis/propuesta/propuesta_iae.tex
separacion de partes de la propuesta en .texs

  \documentclass{llncs}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage[boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate}
\DeclareGraphicsExtensions{.jpg, .png, .mps, .bmp, .pdf}
\usepackage{epsfig}
\usepackage{subfigure}
\newtheorem{Definition}{Definition} 
\newtheorem{Example}{Example} 
\newtheorem{Theorem}{Theorem} 
\newtheorem{Proof}{Proof} 
\newcommand{\denselist}{\topsep 0pt \itemsep -4pt}
\newcommand{\tup}[1]{\langle #1 \rangle}
\newcommand{\vvec}[1]{\mathbf{#1}}
\newcommand{\join}{\bowtie}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\body}{{body}}
\newcommand{\head}{{head}}
\newcommand{\qrule}{:\!\!-}
\newcommand{\arc}{\text{arc}}
\newcommand{\Theory}[1]{T(#1)}
\newcommand{\mcdsat}{\textsc{McdSat}}
\newcommand{\minicon}{{MiniCon}}
\newcommand{\Omit}[1]{}
\newcommand{\citeX}[1]{\citeauthor{#1}~\citeyear{#1}}

\begin{document}
\allowdisplaybreaks
\title{Selecting the Maximum-Utility  Web Services  Using Circuits}
\author{Daniel Izquierdo \inst{1}  and Blai Bonet \inst{1}  and Mar\'{\i}a-Esther Vidal \inst{1}}

\institute{Universidad Sim\'on Bol\'{\i}var\\
                Caracas, Venezuela\\
                \{idaniel,bonet,mvidal\}ldc.usb.ve} \maketitle
\begin{abstract}
In Service Oriented Architectures (SOA), concrete services are described in terms of functionality   and QoS parameters, while software applications are specified as workflows of abstract services and non-functional criteria that establish the  application desirable functionality and  expected quality, respectively.  During workflow execution time,  abstract services  are rewritten 
with the concrete services  that meet the workflow  functional and non-functional restrictions. Since, service selection is done on-the-flight and the space of concrete services may be very large, efficiency and scalability are required.  In this paper we propose the {\it McdSat}$^c$ framework to efficiently solve the problem of service selection in presence of a large number of concrete services.
First, we use the Local As View approach to describe the functionality  of the concrete services in terms of views of abstract services, the quality as an overall utility function that combines the different QoS values that describe the service, and  workflows as  conjunctive queries on abstract services. Based on this representation, we 
model the problem of service selection as a known problem in the area of integration systems referred as query rewriting using views.  We encode the service selection problem as a propositional theory whose models correspond to the composition of the services that implement the abstract workflow and maximizes the overall utility function; known relationships between d-DNNF theories and arithmetic circuits are exploited to provide an efficient and scalable solution.  We report on the performance of our proposed approach, and we observe that  {\it McdSat}$^c$  efficiently scales up to large instances of the service selection problem.

\end{abstract}                
\section{Introduction}
Under the umbrella of the Semantic Web and supported by Service Oriented architectures, the number of Web data sources and services has exploded during the last few years.  For example,  currently, the molecular biology databases
collection includes 1,170 databases~\cite{Galperin09}, that is
95 more than the previous year~\cite{Galperin2008} and 110 more than two years ago~\cite{Galperin2007};  tools
and services as well as the number of instances published by these resources, follow a similar progression~\cite{Benson07}. Thanks
to this wealth, users rely more on various
digital tasks such as data retrieval from public data sources and
data analysis with Web tools or services organized in
complex workflows.

In order to design an application, users usually specify the functionality in terms of a workflow of abstract services, while the desirable quality  is defined by restricting the values of the QoS parameters that describe the concrete available services. To evaluate the proposed workflow,  abstract services are instantiated on concrete services in a way restrictions on the QoS parameters are satisfied.  However, the performance of this tasks is impacted by the number of available sources,  techniques enable to efficiently scale up to a large number of services are required.

In this paper we aim to provide a solution to this problem and provide techniques that efficiently traverse the space of available services and select combinations that meet the functional and non-functional requirements that describe a designed application.  We name our proposed solution {\it MCDSat}$^c$.

In {\it MCDSat}$^c$, concrete service functionalities are decribed as views on abstract services and workflows are represented as conjunctive queries on abstract services; this service representation is similar to the one generated in a semi-automatic way for the {\cal DEIMOS} system ~\cite{AmbiteISWC09}.  In addition, rules that define workflows and  concrete services in the {\it MCDSat}$^c$ catalog,  are created in a way that input and output restrictions of the combined abstract services are satisfied. To represent the QoS measures, each concrete service description is annotated with a real number that represents an overall value of the QoS measures of this service.  Finally, {\it MCDSat}$^c$ models the web service selection problem as the problem of query rewriting using views \cite{halevy:survey}. This problem is important in the context of data integration
\cite{Chen05,JaudoinPRST05}, and query optimization and data maintenance \cite{AfratiLU07,levy:bucket}, and several approaches have been defined to efficiently scale up to a large number of views~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}. In this paper we propose the {\it MCDSat}$^c$ framework which extends the approach proposed in ~\cite{arvelo:aaai06},  with the capability of dealing with constants and identifying the composition of services that maximizes a given utility function.

{\it MCDSat}$^c$  translates an instance of the service selection problem into the problem of enumerating the models of a propositional theory that encodes information about the workflow, the concrete services and the conditions that need to be satisfied in order to generate a composition that maximizes the utility function. This theory is represented as a CNF formula which is compiled into a deterministic
and decomposable negation normal form d-DNNF representation, from which the models that maximizes the overall utility function are obtained in linear time using modern SAT techniques~\cite{darwiche:dnnf}.   
We empirically studied the quality of the {\it MCDSat}$^c$ on variety of benchmarks and we observed  that the proposed technique provides an efficient solution to the service selection problem which is able to scale up to large workflows as well to a large number of views.

 This paper is comprised of six additional sections. The next section motivates our approach by using an example, and  we summarize existing related work in section 3. Section 4 describes the {\it MCDSat}$^c$ system architecture, and  the experimental study is reported in section 5. 
 In section 6 we present the formalization of the web service selection problem as a Propositional Logic theory, and finally, section 7 outlines our conclusions and future work.

\section{Motivating Example}
Consider the abstract and concrete services in Table ~\ref{table:services}  which represent applications in the flight domain.

\begin{table}
\begin{tabular}{| l| l |}
\hline
Abstract Service & Description \\
\hline
$fight(x1,x2)$ & relates cities x1 and x2 if there is a flight between them\\
\hline
$uscity(x1)$ &  determines if a city x1 is a US city\\
\hline \hline
Concrete  Service & Description \\
\hline
$national(x1,y1)$&  returns  two US cities that are connected by  direct flights \\
\hline
$oneway(x1,y1)$ & returns two cites that are connected by one way direct flights \\
\hline
$onestop(x1,y1)$ &  returns  two cites that are connected by one-stop flights \\
\hline
$ flightToCCS(x1,"CCS")$ & returns a city that is connected to  Caracas by a direct flight\\
 \hline
$ onestopToCCS(x1,y1)$ & returns two cites x1 and y1, such that there is  one-stop flight\\ 
 & from city x1 to Caracas stopping at city y1.\\
 \hline
 $fromWAS("WAS",y1)$ &  returns a city y1 to which flights from Washington arrive. \\
 \hline
\end{tabular}
\label{table:services}
\caption{Abstract and Concrete Services}
\end{table}

Using the  Local As View (LAV) approach~\cite{AmbiteISWC09}, concrete services in Table 1 are semantically described as views on the abstract services {\it flight} and {\it uscity} as follows:

\begin{alignat*}{1}
national(x1,y1)\ &\qrule\ flight(x1,y1),\,  uscity(x1),\,  uscity(y1)\,. \\
oneway(x2,y2)\ &\qrule\ flight(x2,y2)\,. \\
onestop(x3,z3)\ &\qrule\ flight(x3,y3),\, flight(y3,z3)\,. \\
flightToCCS(x2,"CCS")\ &\qrule\ flight(x2,"CCS")\,. \\
onestopToCCS(x3,y3)\ &\qrule\ flight(x3,y3),\, flight(y3,"CCS")\,. \\
fromWAS("WAS",y3)\ &\qrule\ flight("WAS",x3)\,. \\
\end{alignat*}

Now suppose a user is interested in implementing a workflow able to retrieve the one-stop round trip flights from US cities to any city in the world, such that flights can stop at any city. 
Consider the following conjunctive query that represents the workflow that defines this request in terms of abstract services. This workflow was defined in way the input parameters of each abstract service are bound by  constants in the workflow, or by attributes projected out by  previous abstract services.

\begin{alignat*}{1}
w(x,y1,y2,y3)\ &\qrule\ flight(x,y1),\, flight(y1,y2),\,  flight(y2,y3),\,  flight(y3,x),\,  \\
                   \ & uscity(x)\,. \\
\end{alignat*}

Implementations of this workflow correspond to compositions of the concrete services where each concrete service can implement a subset of abstract services of the workflow, but each abstract service can be implemented by exactly one concrete service. The following composition of concrete services corresponds to one of the XX implementations of the workflow:

\begin{alignat*}{1}
wi1(x,y1,"CCS",y3)\ &\qrule\ national(x,y1),\, flightToCCS(y1,"CCS"),\,  oneway("CCS",y3),\,  \\
\ & national(y3,x)\,.  \\
\end{alignat*}

However, note that the following compositions are not valid:

\begin{alignat*}{1}
wi2(x,y1,"CCS"y3)\ &\qrule\ national(x,y1),\, flightToCCS(y1,"CCS"),\, \\
\ & fromWAS("WAS",y3),\,  national(y3,x)\,. \\
wi3(x,y1,y2,y3)\ &\qrule\ national(x1,y1),\, onestop(x1,y2),\,  oneway(y2,y3),\,  \\
\ & national(y3,x)\,. \\
\end{alignat*}

The composition {\it wi2} is not valid because  it maps the workflow variable
{\it y2} into constants {\it "CCS"} and {\it "WAS"} which denote different cities.
On the other hand, the composition {\it wi3} does not implement the workflow because the concrete service  {\it onestop} does not receive as input or produce as output, the city where the flight stops (represented by the variable {\it y1}); thus, it is not possible to ensure that the city where this flight stops and the end city  retrieved by the service {\it national}, are the same.

To avoid producing not valid workflow implementations, it is required to handling constants in a way that different constants are not mapped into
each other either directly or indirectly (via transitivity). In addition,  all the attributes in the workflow output  or needed to join other services in the workflow, have to be produced by the selected concrete service.

In addition, suppose each concrete service is annotated with a utility function that aggregates the values of different QoS that characterize the behavior of the service. Then, since the space of valid service compositions of an abstract workflow can be very large, it is required a technique able to identify the ones that maximize the utility function  without having to enumerate the whole set of valid compositions. In this paper, we propose a Propositional logic-based  approach that takes advantage of the  power of  modern SAT solvers, to efficiently enumerate the service compositions that correspond to valid implementations of a given abstract workflow, as well as the compositions that maximize a given utility function.

@@

We have shown how the propositional theory used in McdSat can
be extended to support constants, and how it can be used to 
compute the best rewritings with respect to an additive
cost model. The cost model is simple yet expressive.
The computation of the best models relies on an arithmetic
circuit that is obtained from the d-DNNF of the propositional
theory.

\bibliographystyle{abbrv}
\bibliography{ref}

>>>>

\documentclass{article}

\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage[boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage{enumerate}
\DeclareGraphicsExtensions{.jpg, .png, .mps, .bmp, .pdf}
\usepackage{epsfig}
\usepackage{subfigure}
\newtheorem{Definition}{Definition} 
\newtheorem{Example}{Example} 
\newtheorem{Theorem}{Theorem} 
\newtheorem{Proof}{Proof} 
\newcommand{\denselist}{\topsep 0pt \itemsep -4pt}
\newcommand{\tup}[1]{\langle #1 \rangle}
\newcommand{\vvec}[1]{\mathbf{#1}}
\newcommand{\join}{\bowtie}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\body}{{body}}
\newcommand{\head}{{head}}
\newcommand{\qrule}{:\!\!-}
\newcommand{\arc}{\text{arc}}
\newcommand{\Theory}[1]{T(#1)}
\newcommand{\mcdsat}{\textsc{McdSat}}
\newcommand{\minicon}{{MiniCon}}
\newcommand{\Omit}[1]{}
\newcommand{\citeX}[1]{\citeauthor{#1}~\citeyear{#1}}

\newcommand{\comment}[1]{}

\newcommand{\mcdsatc}{{\it MCDSat}$^c$}

\begin{document}

\comment{
\allowdisplaybreaks
\title{Selección de Servicios Web De Máxima Utilidad Usando Circuitos}
\author{Daniel Izquierdo}

{Universidad Sim\'on Bol\'{\i}var\\
                Caracas, Venezuela\\
                idaniel@ldc.usb.ve} \maketitle

@@

compute the best rewritings with respect to an additive
cost model. The cost model is simple yet expressive.
The computation of the best models relies on an arithmetic
circuit that is obtained from the d-DNNF of the propositional
theory.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{portada}

\tableofcontents
\newpage

\input{planteamiento}
\input{justificacion}
\input{objetivos}
\input{metodologia}
\input{cronograma}

\addcontentsline{toc}{section}{Referencias} 
\bibliographystyle{abbrv}
\bibliography{ref}
